Analyzing Build Logs Using Programming by Example

### 2019-10-01 paper/paper.tex
writing masterplan - first completeish version

\plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)

to combat that users write tools to <extract / retrieve superbegriff> information from build logs.

>>>>

\plan{why are logs so difficult: mention heterogeneous, semi-structured (paper reference for that?), big data (reference paper about log sizes), in distributed systems probably distributed (really also for build log?)
g
to combat that users write tools to <extract / retrieve superbegriff> information from build logs.
